---
output: github_document
---
```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# mipmapper
[![Travis build status](https://travis-ci.org/mrc-ide/mipmapper.svg?branch=master)](https://travis-ci.org/mrc-ide/mipmapper)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/mrc-ide/mipmapper?branch=master&svg=true)](https://ci.appveyor.com/project/mrc-ide/mipmapper)
[![Coverage status](https://codecov.io/gh/mrc-ide/mipmapper/branch/master/graph/badge.svg)](https://codecov.io/github/mrc-ide/mipmapper?branch=master)

The R package *mipmapper* package contains a series of functions for analysing and visualising Molecular Inversion Probe (MIP) data. **This package is in early stages of development**, but will hopefully eventually include a range of population genetic analyses.

### Installation

In R, ensure that you have the devtools package installed by running
```{r, eval = FALSE}
install.packages("devtools", repos='http://cran.us.r-project.org')
```
Then  we can simply install the *mipmapper* package directly from GitHub by running
```{r, eval = FALSE}
devtools::install_github("mrc-ide/mipmapper")
library(mipmapper)
```
And we can load the package by running
```{r}
library(mipmapper)
```

### Example analysis

Load raw data from .csv file. You will need to change the file path to where you have stored the data. An example of this is shown below, but commented out.
```{r}
# dat0 <- fast_read("path_to_your_data/NeutralSNPs_AheroYombo.csv")
dat0 <- fast_read(system.file("extdata", "dummy_data.csv", package = "mipmapper"))
```
Some miscellaneous filtering. Subset to SNPs only (i.e. no more complex mutations), group all alternative alleles together as a single "non-reference" allele, and drop irregular loci (for example non-integer barcode counts).
```{r}
dat1 <- filter_misc(dat0, SNP_only = TRUE, group_Alt = TRUE, drop_irregular = TRUE)
```
Next we want to filter based on coverage, throwing away any loci that are below a minimum coverage level. We can visualise how much data will be left at different thresholds using the following function:
```{r plot_coverage}
plot_coverage(dat1)
```

Choose a threshold that strikes a balance between data quantity and quality. Once you have chosen a threshold, apply the filtering as follows:
```{r}
my_threshold <- 6
dat3 <- filter_coverage(dat1, min_coverage = my_threshold)
```


